sims

### 2024-11-06 sims/sims.Rmd
update sims

## apply function sim_haz
data_single2 <- sim_haz(subj_n = 1, rep_n = 2000) %>%
               mutate(period = bin,
                      trial = str_sub(rep, start=6, end=6)) %>%
               select(-c("contrast","cumsum","outcomel","outcomen","bin","rep")) 
head(data_single2, n=20)
```

@@

@@

```{r}
p12.1 <-ggplot(lifetable2, aes(x = period, y = hazard,
                         colour = condition)) +
  geom_line(linewidth = 1) +
  geom_point(size=3) +
  geom_linerange(aes(ymin=hazard-se_haz, ymax=hazard+se_haz), show.legend = F) +
  scale_colour_brewer(palette = "Dark2") + 
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(limits = c(0,1)) +
  ggtitle("hazard")  +
  xlab("timebin") + ylab("probability")
p12.1
```

@@

```{r}
acc <- tibble(
  time = seq(1,10,1),
  cond1 = rep(1,length = 10),
  cond2 = c(0, 0, 0, 0, 0, 1, 1, 1, 1, 1)
) %>% 
  pivot_longer(-time,
               names_to = "condition",
               values_to = "accuracy") %>% 
  mutate(condition = factor(condition))
head(acc,n=20)
```

@@

```{r}
p12.2 <-ggplot(acc, aes(x = time, y = accuracy,
                         colour = condition)) +
  geom_line(linewidth = 1) +
  geom_point(size=3) +
  scale_colour_brewer(palette = "Dark2") + 
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(limits = c(0,1)) +
  xlab("timebin") +
  ylab("probability") +
  ggtitle("conditional accuracy") 
p12.2
```

@@

ggsave("sims/figures/haz_acc_single.jpeg",
       width = 7, height = 5, dpi=800)

>>>>

## apply function sim_haz
data_single2 <- sim_haz(subj_n = 1, rep_n = 1000) %>%
               mutate(period = bin,
                      trial = as.integer(str_sub(rep, start=4, end=7)),
                      condition = factor(condition, labels=c("congruent","incongruent"))) %>%
               select(-c("contrast","cumsum","outcomel","outcomen","bin","rep"))  %>%
               mutate(acc = ifelse(period<6 & condition=="incongruent",0,1),
                      acc = ifelse(period==6 & condition=="incongruent" & trial < 500,0,acc)) 
head(data_single2, n=20)
summary(data_single2)

@@

## add ca(t)

```{r}
ca <- data_single2 %>% 
    group_by(condition,period) %>%
    summarize(ca = mean(acc) %>% round(digits = 2),
              n = n(),
              .groups = 'drop') %>%
    ungroup() %>%
    mutate(se_ca = sqrt((ca * (1-ca)) / n) %>% round(digits = 3)) 
ca
```

@@

```{r}
p12.1 <-ggplot(lifetable2, aes(x = period, y = hazard,
                         colour = condition)) +
  geom_line(linewidth = 1) +
  geom_point(size=3) +
  geom_linerange(aes(ymin=hazard-se_haz, ymax=hazard+se_haz), show.legend = F) +
  scale_colour_brewer(palette = "Dark2") + 
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(limits = c(0,1)) +
  ggtitle("hazard")  +
  xlab("timebin") + ylab("probability") + guides(color=guide_legend(title="prime type"))
p12.1
```

@@

```{r}
acc <- tibble(
  time = seq(1,10,1),
  congruent = rep(1,length = 10),
  incongruent = c(0, 0, 0, 0, 0, .5, 1, 1, 1, 1)
) %>% 
  pivot_longer(-time,
               names_to = "condition",
               values_to = "accuracy") %>% 
  mutate(condition = factor(condition))
head(acc,n=20)
```

@@

```{r}
p12.2 <-ggplot(ca, aes(x = period, y = ca,
                         colour = condition)) +
  geom_line(linewidth = 1) +
  geom_point(size=3) +
  geom_linerange(aes(ymin=ca-se_ca, ymax=ca+se_ca), show.legend = F) +
  scale_colour_brewer(palette = "Dark2") + 
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(limits = c(0,1)) +
  xlab("timebin") +
  ylab("probability") +
  ggtitle("conditional accuracy") + 
  guides(color=guide_legend(title="prime type"))
p12.2
```

@@

ggsave("sims/figures/haz_acc_single.jpeg",
       width = 7, height = 6, dpi=800)
